---
title: "Wildlife Ecology and Management"
subtitle: "EFB 390: Fall 2022"
author: "Prof. [Elie Gurarie](https://eligurarie.github.io/)"
output: 
  rmdformats::readthedown:
    toc_depth: 5
    thumbnails: TRUE
    anchor_sections: FALSE
---


```{r, echo=FALSE, eval = TRUE}
htmltools::img(src = "assets/ESFStacked_Full color.png", alt = 'banner', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:150px')
```


## Course Materials

Taught by Dr. [Elie Gurarie](https://www.esf.edu/faculty/gurarie/).  This page contains lectures, assignments and other resources.  [**Jump to latest unit**](#where-are-the-animals-and-why).


#### Class basics

- [Highlights of the Syllabus](lectures/HighlightsOfTheSyllabus.html) ([pdf](pdfs/Lecture00_HighlightsOfTheSyllabus.pdf))


## Lectures

### Unit I. Basics and history
#### *What do animals mean to us?*

- [1: Basics and Definitions](lectures/Lecture01/Lecture_Basics.html) ([pdf](pdfs/Lecture01_Basics.pdf))
- [2: Deep Human-Wildlife History](lectures/Lecture02/Lecture02_DeepHistory.html)  ([pdf](pdfs/Lecture02_DeepHistory.pdf))
- [3: Human-Wildlfe History - Part II](lectures/Lecture03/Lecture03_HistoryPartII.html)  ([pdf](lectures/Lecture03/Lecture03_HistoryPartII.pdf))
- [HW1: Wildlife in the News (results)](assignments/Results.html)


### Unit II. Estimation and Sampling
#### *How many animals are there?*

- [4: Counting Animals - Part I](lectures/Lecture04/Lecture04_CountingAnimals.html) ([pdf](lectures/Lecture04/Lecture04_CountingAnimals.pdf))
- [5: Counting Animals - Part II](lectures/Lecture05/Lecture05_CountingAnimals_PartII.html) ([pdf](lectures/Lecture04/Lecture04_CountingAnimals.pdf))
- [6a: Counting Animals - Sampling Uncertainty](lectures/Lecture06/Lecture06a_CountingAnimals_Uncertainty.html) ([pdf](lectures/Lecture06/Lecture06a_CountingAnimals_Uncertainty.pdf))
- [6b: Example of Antarctic Ice Seals](lectures/Lecture06/Lecture06b_EstimatingAntarcticIceSeals.pdf)
- [6c: Intro to Mark-Recapture](lectures/Lecture06/Lecture06c_MarkRecapture_OphelieCouriot.pdf) (guest lecture by [Dr. Ophélie Couriot](https://sites.google.com/view/opheliecouriot/cv))
- [7: More on Mark-Recapture and Index Counts](lectures/Lecture07/Lecture07_IndexCounts.html) ([pdf](lectures/Lecture07/Lecture07_IndexCounts.pdf))

### Unit III. Ranges, Habitats, Niches
#### *Where are the animals?  And Why?*

- [8: Ranges and Habitats](lectures/Lecture08/Lecture_Habitat_PartI.html) ([pdf](lectures/Lecture08/Lecture_Habitat_Part1.pdf))
- [9: Niches and Habitats](lectures/Lecture09/Lecture09_NichesAndHabitats.html) ([pdf](lectures/Lecture09/Lecture09_NichesAndHabitats.pdf))
- [9b: Caribou Habitat Selection - Guest Lecture Gurarie (pdf)](lectures/Lecture09/Lecture09b_Gurarie_PorcupineHabitatSelection.pdf)
- [10: Modeling Everything (but especially habitats)](lectures/Lecture10/Lecture_Modeling.html) ([pdf](lectures/Lecture10/Lecture10_Modeling.pdf))


### Unit IV. Population Ecology
#### *Why are there as many as there are?*

- [11a: Part I - Exponential Growth](lectures/Lecture11/Lecture_PopulationEcology.html) ([pdf](lectures/Lecture11/Lecture_PopulationEcology_PartI.pdf))
- [11b: Part II - Limits to Growth](lectures/Lecture11/Lecture_PopulationEcology_PartII.html) ([pdf](lectures/Lecture11/Lecture_PopulationEcology_PartII.pdf))
- [11c: Part III - All the Rest of Population Ecology**](lectures/Lecture11/Lecture_PopulationEcology_PartIII.html) ([pdf](lectures/Lecture11/Lecture_PopulationEcology_PartIII.pdf))


### Unit V. The North American Model of Wildlife Conservation

- [12: The North American Model of Wildlife Conservation](lectures/Lecture12/Lecture_NAM.html) ([pdf](lectures/Lecture12/Lecture_NAM.pdf))

```{r, echo = FALSE, eval = FALSE}
# renderthis::to_pdf("file.rmd")
```

### Guest Lectures

- Eaqan Chaudhry: [**Cottontail Stress, Habitat Use and Survival**](lectures/GuestLectures/Chaudhry_guestlecture_EFB390.pdf)
-  Dr. Michael Schummer: [**Migratory Bird Ecology and Management**](lectures/GuestLectures/Schummer_MigratoryBirdEcologyAndManagement.pdf)
-  Riley Stedman: [**Habitat Selection of Mallards and Black Ducks in Eastern Long Island**](lectures/GuestLectures/Stedman_Habitat selection of Ducks on Eastern Long Island.pdf)


### Exam II: Readings

- are [here](https://drive.google.com/drive/folders/1A-QLapqbN2C4RJ-1j_-TLq7iIeCg3uNN?usp=sharing)

<!-- 
instructions:
git push origin gh-pages

Or, to merge with (non-existent) main:
1. git checkout gh-pages
2. git merge main
3. git checkout main
--> 
