---
title: "Wildlife Ecology and Management"
subtitle: "EFB 390: Fall 2022"
author: "Prof. [Elie Gurarie](https://eligurarie.github.io/)"
output: 
  rmdformats::readthedown:
    toc_depth: 5
    thumbnails: TRUE
    anchor_sections: FALSE
---


```{r, echo=FALSE, eval = TRUE}
htmltools::img(src = "assets/ESFStacked_Full color.png", alt = 'banner', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:150px')
```


## Course Materials

Taught by Dr. [Elie Gurarie](https://www.esf.edu/faculty/gurarie/).  This page contains lectures, assignments and other resources. 

## Lectures

- [0: Highlights of the Syllabus](lectures/HighlightsOfTheSyllabus.html) ([pdf](pdfs/Lecture00_HighlightsOfTheSyllabus.pdf))

### Unit I. Basics and history

- [1: Basics and Definitions](lectures/Lecture01/Lecture_Basics.html) ([pdf](pdfs/Lecture01_Basics.pdf))
- [2: Deep Human-Wildlife History](lectures/Lecture02/Lecture02_DeepHistory.html) ([pdf](pdfs/Lecture02_DeepHistory.pdf))
- [3: Human-Wildlfe History - Part II](lectures/Lecture03/Lecture03_HistoryPartII.html) ([pdf](lectures/Lecture03/Lecture03_HistoryPartII.pdf))
- [HW1: Wildlife in the News (results)](assignments/Results.html)


### Unit II. Estimation and Sampling

- [4: Counting Animals - Part I](lectures/Lecture04/Lecture04_CountingAnimals.html)([pdf](lectures/Lecture04/Lecture04_CountingAnimals.pdf))


```{r, echo = FALSE, eval = FALSE}
# renderthis::to_pdf("file.rmd")
```

<!--
instructions:
git push origin gh-pages

Or, to merge with (non-existent) main:
1. git checkout gh-pages
2. git merge main
3. git checkout main
--> 
