---
title: 'Tasmanian Devil Solutions'
subtitle: 'EFB 370 - Spring 2023'
author: "E. Gurarie, E. Khadonova"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
    toc_float: true
---


> There are THREE exercises in this lab to submit by midnight next Monday, March 20.  

```{css, echo = FALSE}
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 16px;
    color: darkgreen;
    font-family: "Garamond";
    background: #DFD;
    border-left: 5px solid #262; 
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, message = FALSE, warning = FALSE, echo = FALSE}
require(expm)
require(gplots)
require(plyr)
require(magrittr)
require(utils)
library(DiagrammeR)
source("leslie_diagram.R")
library(magic)
```

## 3. Tasmanian Devil

Pre infectious facial tumor disease, the life history populaiton matrix for Tasmanian devils looked something like this:

```{r}
par(mar = c(0,0,0,0))
M.pre <- rbind(c(0,.1,.5,.7),
               c(.7,0,0,0),
               c(0,.8,0,0),
               c(0,0,.8,.5))
leslie_diagram(M.pre, stages = c("0", "1", "2", ">3"))

```

> # **Homework Assignment** 
> ## (Due: Thursday, March 23)
>
> After facial tumor disease emerged and established itself in the Tasmanian devil population, annual mortality of 2 year olds and 3-plus year olds skyrocketed to 90%. This had an immediate impact on the population growth factor $\lambda$.   
> 
> 1. (**3 pts.**) Changing only those survival probabilities, what is the new population growth factor? What is the new stable age distribution? 

```{r}
par(mar = c(0,0,0,0))
M.post <- rbind(c(0,.1,.5,.7),
               c(.7,0,0,0),
               c(0,.8,0,0),
               c(0,0,.1,.1))
eigen.post <- eigen(M.post)
leslie_diagram(M.post, stages = c("0", "1", "2", ">3"))

(lambda.post <- Re(eigen.post$values)[1])
(Nstar.post <- Re(eigen.post$vector)[,1] %>% {.; ./sum(.)}) %>% round(2)
```

> 2. (**2 pts.**) As a population-level response, Tasmanian devils radically increased the number of "precocial" births, i.e. 1 yr olds that reproduce.  How high must 1 year old birth rates become to rescue the Tasmanian devil population?   

Guess & check, somewhere around **0.97**. 

```{r}
par(mar = c(0,0,0,0))
M.post2 <- rbind(c(0,.97,.5,.7),
               c(.7,0,0,0),
               c(0,.8,0,0),
               c(0,0,.1,.1))
eigen.post <- eigen(M.post2)
(lambda.post <- Re(eigen.post$values)[1])

leslie_diagram(M.post2, stages = c("0", "1", "2", ">3"))
```


New distribution:
```{r}
(Nstar.post <- Re(eigen.post$vector)[,1] %>% {.; ./sum(.)}) %>% round(2)
```
 
> **Extra credit:** Can a **stable age distribution** have higher proportions of older animals?  Explain why or why not? 

Yes - but only if the population is falling so rapidly that there are fewer younger cohorts being born than adults giving birth. 
